Aa Language Reference Manual

### 2016-03-18 v2/Ahir-asm/devel/docs/AaLRM.tex
Lots of clean up.  Moved critical examples to regression-tests folder. Can we automate the regression testing?
Also lots of clean up around the PHI handling.  We will treat the
PHI block as a set of concurrent statements.  This allows for
cleaner handling, and why would you want to have dependencies
across the PHI's anyway.

@@

>>>>

\subsubsection{Careful! The phi-statements in a merge block are concurrent}

Note that the phi-statements in a merge are concurrent, and
may execute in any order.
An example:
\begin{verbatim}
  $merge loopback $entry // $entry is the entry place
     $phi p := 0 $on $entry np $on loopback
     $phi q := 0 $on $entry p  $on loopback
  $endmerge
\end{verbatim}
In this case, the two $phi$ statements may execute
in any order, and thus the value on $q$ after the execution
is indeterminate.  To prevent such race conditions, do not
use the result of a $phi$ as an input to another $phi$ in
the same merge block.

@@

\section{Specifying buffering for expressions}

By default, the result of each expression may be
buffered by the AHIR compilers.  The default amount of
buffering is $1$.  If you wish to specify more buffering, 
say $2$ units, then we add 
\begin{verbatim}
$buffering 2
\end{verbatim}
after the expression.

For example
\begin{verbatim}
( A $buffering 2  + (B + C) $buffering 3) $buffering 2
\end{verbatim}
means that the expression $A$ has buffering $2$,
the expression $(B+C)$ has buffering $3$ and the
overall expression $(A + (B+C))$ has buffering $2$.
